Global Namespaces Scale as Well as Decoupled Namespaces

### 2017-02-22 paper/paper.tex
paper: add microbenchmarks
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Cudele as a Programmable Storage System}

% Programmability
We use a programmable storage approach to expose internal subsystem
abstractions as ``interfaces" for applications to create higher level
functionality and services.

\subsubsection{No Changes: Turning Knobs}

@@

Re-using the debugging and testing features in the storage system, we can turn
``stream" on and off. If it is off, then the metadata servers will not save
journals in the object store and the daemons that apply the journal to the
metadata store will never run. Performance numbers for enabling and disabling
the stream phase are presented back in Section~\S\ref{sec:fault-tolerance}.

\subsubsection{External Library: Reads/Writes Journal Events}

@@

\subsubsection{Storage System Changes: Volatile Merge}

@@

% How it works: socket for changing daemon's internal state (debugging, logging, behaviour)
% 1. API for putting state into the daemon dynamically
% 2. Documentation all the tunables
% 3. Hooks directly into daemon code so we can use any parsing functionality in there

% What we actually implemented
Of these 6 mechanisms only 4 had to implemented. ``RPCs" and ``Stream" can be
achieved with tunables in configuration files for the storage system (e.g., metadata cache size,
logging on/off, etc.). 
``Persist", ``Save", and ``Create" are implemented in
separate programs and libraries and do not require modifications to the storage
system. ``Volatile Apply" requires changes to the metadata server to inject
updates back into the global namespace.

% Outline of the section
In this section, we describe how we decoupled the consistency and fault
tolerance policies from their mechanisms to allow applications to choose the
semantics they need. Each section corresponds ot the labeled arrows in
Figure~\ref{fig:decouple}.

\subsection{RPCs (Existing CephFS Implementation)}

CephFS uses round-trip remote procedure calls (RPCs) for most of

\subsection{Stream (Existing Implementation)}

\subsection{Create}

%- How we leverage it

\subsection{Volatile Apply (v.apply)}
\label{sec:vapply}
\subsection{Save}
\label{sec:save}
\subsection{Persist}
\label{sec:persist}

\section{Results}
\subsection{Microbenchmarks}

>>>>

\subsection{Subtree Policies}

% Outline of the section
Each section below corresponds ot the labeled arrows in
Figure~\ref{fig:decouple}. This implementation decouples policies from
mechanisms allowing applciations to choose the consistency and fault tolerance
semantics they need.

% Programmability
Of the 6 mechanisms in Figure~\ref{fig:decouple} 4 had to implemented and only
1 required changes to the underlying storage system itself.  RPCs and stream
can be achieved with tunables in configuration files for the storage system
(e.g., metadata cache size, logging on/off, etc.).  Persist", save, and create
are implemented as library and does not require modifications to the storage
system. Volatile apply requires changes to the metadata server to inject
updates back into the global namespace.

\subsection{No Changes: RPCs, Stream}

@@

Re-using the debugging and testing features in the storage system, we can turn
stream on and off. If it is off, then the metadata servers will not save
journals in the object store and the daemons that apply the journal to the
metadata store will never run. Performance numbers for enabling and disabling
the stream phase are presented back in Section~\S\ref{sec:fault-tolerance}.

\subsection{External Library: Create, Save, Persist}
%Reads/Writes Journal Events}

@@

\subsection{Storage System Changes: Volatile Merge}

@@

% How it works: socket for changing daemon's internal state (debugging, logging, behaviour)
% 1. API for putting state into the daemon dynamically
% 2. Hooks directly into daemon code so we can use any parsing functionality in there
% 3. Documentation all the tunables

% 1. read journal of updates from file
% 2. call replay (uses same code as when an MDS comes back) on each event
% 3. skip inodes so MDS doesn't hand out those new inodes

\section{Results}
\subsection{Microbenchmarks}
\begin{figure*}[tb]
\centering
\includegraphics[width=180mm]{figures/results-microbenchmark.png}
\caption{Here's a graph.}
\end{figure*}

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/results-files.png}
\caption{Here's a graph.}
\end{figure}
